Continuous gravitational waves in the lab: recovering audio signals with a table-top~optical microphone

### 2021-09-25 paper/ifo-singleTone.tex
editor comments

A tone with a frequency of $2.09\,{\rm Hz}$ is played through the speaker for one minute. 
The amplitude of the Fourier transform of the recovered signal is shown in Fig.~\ref{fig:webcam_spectrum}. The Discrete Fourier transform is calculated using the NumPy package for Python (see Appendix~\ref{app:code}).
We measured a peak amplitude at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$.
Two harmonics can also be seen at integer multiples of the peak frequency. 
The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo}.
Also, note that the noise appears to rise at lower frequencies, however the origin of this noise is not known.

>>>>

A tone with a frequency of $2.09\,{\rm Hz}$ is played through the speaker for one minute. 
The amplitude of the Fourier transform of the recovered signal is shown in Fig.~\ref{fig:webcam_spectrum}. The discrete Fourier transform is calculated using the NumPy package for Python (see Appendix~\ref{app:code}).
We measured a peak amplitude at $2.099\,{\rm Hz}$ with a full width half maximum (FWHM) of $0.033\,{\rm Hz}$.
Two harmonics can also be seen at integer multiples of the peak frequency. 
The peaks at $4.19\,{\rm Hz}$ and $6.28\,{\rm Hz}$ have amplitudes of $0.103$ and $0.098$ as a fraction of the height of the main peak, respectively. They are likely due to the nonlinear response of the system discussed in Section~\ref{sec:ifo}.
Also, note that the noise appears to rise at lower frequencies; however the origin of this noise is not known.

### 2021-09-25 paper/ifo-tableTopGWs.tex
editor comments

Sound is a commonly used analogy when explaining gravitational-wave science. 
Gravitational-wave signals from binary black hole and neutron star mergers can be converted to audio signals~\footnote{When introducing the acoustic analogy to lay audiences, it is important to emphasize that gravitational waves are not sound. For example, gravitational waves can propagate in a vacuum, whereas sound cannot. Gravitational waves also travel at the speed of light and are not longitudinal waves.} to aid in explanations.
Detection and analysis techniques used by the gravitational-wave community can be demonstrated using table-top equipment (see Ref.~\cite{TTExhibit:2021} as well as the further reading section in the Supplementary Material for a selection of other table-top Michelson interferometer designs used for science communication).
Sound vibrations provide a simple means to move the components of a demonstration interferometer, changing the length of the interferometer arms, and therefore the interference pattern.
We use audio signals throughout this work to simulate gravitational wave--like signals.

>>>>

Sound is a commonly used analogy when explaining gravitational-wave science. 
Gravitational-wave signals from binary black hole and neutron star mergers can be converted to audio signals~\footnote{When introducing the acoustic analogy to lay audiences, it is important to emphasize that gravitational waves are not sound. For example, gravitational waves can propagate in a vacuum, whereas sound cannot. Gravitational waves also travel at the speed of light and are not longitudinal waves.} to aid in explanations.
Detection and analysis techniques used by the gravitational-wave community can be demonstrated using table-top equipment (see Ref.~\cite{TTExhibit:2021} as well as the further reading section in the Supplementary Material for a selection of other table-top Michelson interferometer designs used for science outreach).
Sound vibrations provide a simple means to move the components of a demonstration interferometer, changing the length of the interferometer arms, and therefore the interference pattern.
We use audio signals throughout this work to simulate gravitational wave--like signals.

### 2021-09-25 paper/ifo-wanderingTone.tex
editor comments

A continuous-wave signal may wander slowly (and randomly) in frequency over time, due to stochastic internal processes in the superfluid interior of isolated neutron stars, or variable accretion from a stellar companion for neutron stars in binaries as in LMXBs (see Ref.~\cite{SuvorovaEtAl:2017} and references therein).
Although continuous gravitational waves are nearly monochromatic, the long observing times ($\sim 1\,{\rm yr}$) mean that searches are sensitive to very small frequency drifts. 
A typical observation involves $1 \times 10^{10}$ wave cycles, and a coherent search must track the phase to better than half a cycle over the full observation. 
Here we consider the audio analog of a tone that wanders in frequency.

@@

Fig.~\ref{fig:viterbi} represents a spectrogram with $N_t$ time bins and $N_f$ frequency bins.
The circlular nodes represent the elements of the time and frequency grid, which are labelled as  
$t_i$ and $f_j$, respectively where $i=0,1,2,\mathellipsis,N_t$ and $j=0,1,2,\mathellipsis,N_f$. 
The shading of the nodes represents the detection statistic $F(t_i,f_j)$ (the observable) at each grid point, where dark corresponds to lower values and light to higher values.

>>>>

A continuous-wave signal may wander slowly (and randomly) in frequency over time, due to stochastic internal processes in the superfluid interior of isolated neutron stars, or variable accretion from a stellar companion for neutron stars in binaries such as LMXBs (see Ref.~\cite{SuvorovaEtAl:2017} and references therein).
Although continuous gravitational waves are nearly monochromatic, the long observing times ($\sim 1\,{\rm yr}$) mean that searches are sensitive to very small frequency drifts. \han{note}
A typical observation involves $1 \times 10^{10}$ wave cycles, and a coherent search must track the phase to better than half a cycle over the full observation. 
Here we consider the audio analog of a tone that wanders in frequency.

@@

Fig.~\ref{fig:viterbi} represents a spectrogram with $N_t$ time bins and $N_f$ frequency bins.
The circlular nodes represent the elements of the time and frequency grid, which are labelled as  
$t_i$ and $f_j$, respectively, where $i=0,1,2,\mathellipsis,N_t$ and $j=0,1,2,\mathellipsis,N_f$. 
The shading of the nodes represents the detection statistic $F(t_i,f_j)$ (the observable) at each grid point, where dark corresponds to lower values and light to higher values.
